---
title: "Part I - Data Visualisation"
output: html_document
---

# Import tidyverse, demandData.csv and convert to tibble structure
```{r}
library(tidyverse)
demand = read.csv("demandData.csv")
demand = as_tibble(demand)
```

# Gather dates and pallets into two columns
```{r}
demand_gather = gather(demand,key="Dates",value="Pallet",starts_with("X"))
demand_gather$Dates = substr(demand_gather$Dates,2,11)
demand_gather
```

# Parse date time
```{r}
library(lubridate)
demand_gather$Dates=parse_date_time(demand_gather$Dates,"d.m.Y")
demand_gather
```

# Overall Pallet distribution across 4 weeks
```{r}
demand_gather$Day=as.factor(day(demand_gather$Dates))
demand_group = group_by(demand_gather,Day)
demand_summarise = summarise(demand_group,Pallet=sum(Pallet,na.rm=TRUE))
g = ggplot(demand_summarise)+geom_bar(aes(x=Day,y=Pallet),stat="identity",fill="orange")
g = g + labs(title = "Total pallets across all stores in 4 weeks", subtitle = "Day 1 = Monday", y="Number of pallets per day")
plot(g)
```
- Weekdays are fairly evenly distributed
- No delivery of pallets on Sunday
- Much less pallets delivered on Saturday (half of a weekday)

# Distribution across 4 weeks for Pak 'n Save Botany
```{r}
demand_grouped = group_by(demand_gather,ï..Supermarket,Dates)
demand_summarised = summarise(demand_grouped,Pallet=ceiling(median(Pallet,na.rm=TRUE)))
one_shop = filter(demand_summarised,ï..Supermarket=="Pak 'n Save Botany")
g1 =ggplot(one_shop)+geom_bar(aes(x=Dates,y=Pallet),stat="identity")
```
- Saturday much less, Sunday no pallets

```{r}
supermarket_groups = group_by(demand_gather,Type.of.Supermarket)
supermarket_summarise = summarise(supermarket_groups,Pallet=ceiling(median(Pallet,na.rm=TRUE)))
g2 = ggplot(supermarket_summarise)+geom_bar(aes(x=Type.of.Supermarket,y=Pallet),stat="identity")
g2 = g2 + labs(title = "Median number of pallets per day for each type of supermarket", x = 'Type of supermarket', y= 'Median number of pallets per day')
plot(g2)
```


# Import leaflet, FoodstuffLocations.csv as tibble
```{r}
library(leaflet)
locations = read.csv("FoodstuffLocations.csv")
locations = as_tibble(locations)
```

# Make map of locations
```{r}
map = leaflet(locations)
shop = makeIcon("location.png","location.png", 30, 30)
map %>% addTiles() %>% addMarkers(~Long, ~Lat, icon = shop)
```

```{r}
library(s20x)
boxplot(Pallet ~ Type.of.Supermarket, data = demand_gather, main ="number of Pallets delivered to each type of supermarket per day")
summaryStats(Pallet ~ Type.of.Supermarket, data = demand_gather)

onewayPlot(Pallet ~ Type.of.Supermarket, data = demand_gather)
```

